figures_manuscript

### 2025-07-17 pub_figures/manuscript-figures.Rmd
scatter pdf

res_comb$symbol2 <- anno[res_comb %>% rownames(),"geneSymbol"]
  blue_red_genes <- c(deg_list$pcry$deg_pcry_BLvD.vs.WT_BLvD,
                    deg_list$pcry$deg_pcry_RvD.vs.WT_RvD) %>%
  unique()

@@

# Fig. X
```{r 3_groups, eval=FALSE, fig.show='hold', fig.width=6, fig.height=4, dpi=300, out.width="50%"}

>>>>

res_comb$symbol2 <- anno[res_comb %>% rownames(),"geneSymbol"]
res_comb$id.symbol <- anno[res_comb %>% rownames(),"id.symbol"]

  blue_red_genes <- c(deg_list$pcry$deg_pcry_BLvD.vs.WT_BLvD,
                    deg_list$pcry$deg_pcry_RvD.vs.WT_RvD) %>%
  unique()

@@

# Fig. 5: pCRY interaction partner
## load csv
```{r load_interaction}
top20 <- read.csv2("../UniProt-and-Cre-ID's.csv")
top20_id <- top20$'Cre.ID' %>% str_remove_all(pattern=" ")
summary(top20_id %in% anno$gene_id)

## Plot interaction counts
```{r plot_interaction}
## Interaction genes all-in-one
fig <- "Fig5"
goi_interaction <- top20_id
anno_interaction <- anno[top20_id,]

goi <- anno_interaction
l <- nrow(goi)
all_counts <- {}
for (i in 1:l){
  d <-  plotCounts(dds, gene=goi[i,"gene_id"], intgroup=c("condition","experiment","treatment","genotype"), col=col,main=res$SYMBOL[i],returnData=TRUE)
  d$Gene <- rep(goi[i,"id.symbol"],length(rownames(d)))
  d$sample <- rownames(d)
  rownames(d) <- {}
  all_counts <- bind_rows(all_counts,d)
  }

all_counts$Gene <- factor(all_counts$Gene)
all_counts$Gene <- fct_reorder(all_counts$Gene, all_counts$count, .fun = median, .desc = TRUE)
levels(all_counts$Gene)

# all_counts$Gene <- factor(all_counts$Gene, levels = c("PHOT1","CHR1","CHR2","HKR1","UVR8","DCRY1","PCRY1","ACRY1")) # "DCRY2", 
# levels(all_counts$Gene)

# Plot
max_val <- 1.0*max(all_counts$count)
gcounts_interaction <- ggplot(all_counts, aes(x = Gene, y = count, fill=condition)) +
  geom_boxplot(fatten = 1) +
  scale_fill_manual(values = group.colors) +
  labs(title = "Interaction partners") + 
  theme_bw() +
  removeGrid(x=T, y=T) +
  geom_vline(xintercept=seq(1,length(levels(all_counts$Gene))-1,1)+.5,color="grey") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_y_continuous(trans = "log2") & plot_annotation(title = colData(dds)$experiment[1])
gcounts_interaction %>% print()

ggsave(paste(fig,"_",colData(dds)$experiment[1],"_Counts_Interaction.pdf",sep=""), plot = gcounts_interaction,
width = 15,
height = 8)

## scatter plot
```{r interaction_scatter}
# Interaction
df <- res_comb[anno_interaction$gene_id,]

gg_interaction <- ggplot(df, aes(x=l2FC.WT_blue, y=l2FC.WT_red, label=id.symbol)) + # color=group, fill=group 
    geom_segment(aes(x = l2FC.WT_blue, y= l2FC.WT_red, xend = l2FC.pcry_blue,yend = l2FC.pcry_red, color = l2FC.dd_red),
        arrow = arrow(length = unit(0.01,units = "npc"))) +
  scale_color_gradient2(mid="grey") +
  geom_point(aes(x=l2FC.WT_blue, y=l2FC.WT_red, fill="WT"),shape=21, col="grey40") +
  geom_point(aes(x=l2FC.pcry_blue, y=l2FC.pcry_red, fill = "pcry"),shape=21, col="grey40") +
  scale_fill_manual(name="Genotype",values=c("green3","grey")) + 
  geom_hline(yintercept = c(-1,1), linewidth = 0.1) + 
  geom_vline(xintercept = c(-1,1), linewidth = 0.1) +
  geom_abline(slope=c(1), intercept = 0, linewidth = 0.1) +
  # coord_cartesian(xlim=c(-2,2),ylim = c(-2,2)) +
  coord_fixed(xlim=c(-2,2),ylim = c(-2,2)) +
  geom_text_repel(size=3, max.overlaps = 20) +
  theme_bw() +
  removeGrid(x=T, y=T)
gg_interaction

ggsave(paste(fig,"_",colData(dds)$experiment[1],"_Scatter_Interaction.pdf",sep=""), plot = gg_interaction,
width = 10,
height = 10)

write_xlsx(data.frame(df),"Interaction_results.xlsx")

# Fig. Y
```{r 3_groups, eval=FALSE, fig.show='hold', fig.width=6, fig.height=4, dpi=300, out.width="50%"}
